On the eletrodynamic of moving bodies

### 2019-09-11 Article_AS.Rmd
modif discussion

|Rank correlation  |Rho  |P-value |
|:-----------------|----:|:-------|
|Density residus   | 0.57|8.7^-09^|
|Variability index | 0.08|0.43    |
|$b_0$             | 0.70|2.2^-16^|
|$b_1$             | 0.80|2.2^-16^|
|$b_2$             | 0.60|2.2^-16^|
Table: Sperman’s Rang correlation

@@

Heritability is higher in each site separately than that of the combined sites for all traits (fig 9). Wood density is the only character with strong heritability for each of the sites as well as for the combined sites. The annual ring width and the parameter $b_0$ have low heritability. When parameters $b_1$ and $b_2$, their heritability is very low. The uniformity index has almost zero heritability regardless of the study site.\

@@

Like the density profiles, variability index is different between the two sites, despite the fact that they are the same families of trees. Since the variability index is calculated from the model residuals, the difference can be explained by the fact that the variability that is related to the internal control of the trees has been subtracted from the model and that the remaining one is more controlled by external phenomena related to the study sites. Variability index being more under environmental control than genetic, this explain the lack of heritability of this index. It is not surprising that the variability index is under environmental control because density is mainly controlled by genetics but partly also by growth that is mainly controlled by environmental conditions. The model has made it possible to subtract the typical pattern of the density variation which is related to the internal functioning of the tree [@Lachenbruch2011] and thus under genetic control. Once the portion of the variation under genetic control is subtracted, the rest of the variability can only be of a pedoclimatic order.\

Variability index being different between the sites, as one would expect Spearman's rank coefficient of correlation is not significant (p-value = 0.43; rho = 0.08) for this index. This coefficient value is in agreement with the previous results which show a difference between the two sites and the fact that the variability index is under environmental control. The similarity of the correlation coefficient between the three parameters is explained by the fact that the model adapts well to each of the two sites taking into account the extreme variability of the different density profiles.\

With regard to heritability of density, it is high at both sites. This strong density heritability is similar to previous studies in white spruce [Nelson 1963 in @mothe1983; @Corriveau1991; @Yanchuk1993; @Ivkovich2002a; @Ivkovich2002b; @Beaulieu2006]. All of these studies reported values between 0.36 and 0.80. 
In contrast to density, annual ring width has low to moderate heritability in each site and also for combined sites. This result, which is in agreement with previous studies [@Corriveau1991; @Ivkovich2002a], is explained by the difference we observe when we take the sites separately and when they are combined can be explained by a genotype-environment interaction [@kremer1986], this happens when conditions from one environment to another do not have the same effect on the genotype. This result suggests that, if trees are to be selected for reforestation as a result of this study, the territory be divided into relatively homogeneous subunits, within which the recommended sources will be able to keep their superiority and can be used without risk of maladjustment [@beaulieu1989stabilite].

The parameters of the model, as for them, they have a low heritability either for each site separately or for the combined sites. The parameter $b_0$, has a higher heritability than the other parameters but remains low. This can be explained by the fact that this parameter is very little influenced by cambial age. In fact, $b_0$ is the ordinate at the origin and thus little influenced by the sites (environmental conditions).
The index of variability has almost no heritability. It is not surprising that this trait has very low heritability because it is estimated from model residuals after subtracting the typical density profile.
Our study includes limitations for identifying families that may have low variability in wood density as part in tree improvement programs. Future studies should focus on the resilience and variability associated with one-time events such as short-term water stress. In addition, the trees used for this study are relatively young, we can be interested in older trees.

>>>>

|Rank correlation  |Rho  |P-value |
|:-----------------|----:|:-------|
|Density residus   | 0.57|8.7^-09^|
|Index V           | 0.08|0.43    |
|$b_0$             | 0.70|2.2^-16^|
|$b_1$             | 0.80|2.2^-16^|
|$b_2$             | 0.60|2.2^-16^|
Table: Sperman’s Rang correlation

@@

Heritability is higher in each site separately than that of the combined sites for all traits (fig 9). Wood density is the only character with strong heritability for each of the sites as well as for the combined sites. The annual ring width and the parameter $b_0$ have low heritability. When parameters $b_1$ and $b_2$, their heritability is very low. The index V has almost zero heritability regardless of the study site.\

@@

Like the density profiles, index V is different between the two sites, despite the fact that they are the same families of trees. Since the index V is calculated from the model residuals, the difference can be explained by the fact that the variability that is related to the internal control of the trees has been subtracted from the model and that the remaining one is more controlled by external phenomena related to the study sites. Index V being more under environmental control than genetic, this explain the lack of heritability of this index. The model has made it possible to subtract the type II pith-to-bark profile of the density variation which is related to the internal functioning of the tree [@Lachenbruch2011] and thus under genetic control. Once the portion of the variation under genetic control is subtracted, the rest of the variability can only be of a pedoclimatic order.\

Index V being different between the sites, as one would expect Spearman's rank coefficient of correlation is not significant (p-value = 0.43; rho = 0.08) for this index. This coefficient value is in agreement with the previous results which show a difference between the two sites and the fact that the index V is likely under environmental control. The similarity of the correlation coefficient between the three parameters is explained by the fact that the model adapts well to each of the two sites. Spearman's Rank Correlation Coefficient highlights the interaction between family and environment. The interaction is more or less important from one factor to another probably because some factors are more controlled by the environment and others by genetics.\

Genetic parameter estimates were used to evaluate the variation of density as a selection trait for wood quality. With regard to heritability of density, it is high at both sites. This strong density heritability is similar to previous studies in white spruce [Nelson 1963 in @mothe1983; @Corriveau1991; @Yanchuk1993; @Ivkovich2002a; @Ivkovich2002b; @Beaulieu2006]. All of these studies reported values between 0.36 and 0.80. Average density of our data is therefore highly controlled by genetics as might be expected.
In contrast to density, annual ring width has low to moderate heritability in each site and also for combined sites. This result, which is in agreement with previous studies [@Corriveau1991; @Ivkovich2002a], is explained by the difference we observe when we take the sites separately and when they are combined can be explained by a genotype-environment interaction [@kremer1986], this happens when conditions from one environment to another do not have the same effect on the genotype. This result suggests that, if trees are to be selected for reforestation as a result of this study, the territory be divided into relatively homogeneous subunits, within which the recommended sources will be able to keep their superiority and can be used without risk of maladjustment [@beaulieu1989stabilite].
The parameters of the model, as for them, they have a low heritability either for each site separately or for the combined sites. The parameter $b_0$, has a higher heritability than the other parameters but remains low. This can be explained by the fact that this parameter is very little influenced by cambial age because it is described the density close to pith. In fact, $b_0$ is the ordinate at the origin and thus little influenced by the sites (environmental conditions). Since parameters $b_1$ and $b_2$ are the parameters that describe the change in density over the years of tree growth, they are more likely to be influenced by environmental conditions.
The index V has a heritability close to zero for each of the sites (Asselin 6.10^-6^ and Saint-Casimir 3.10^-6^) and the two sites combined (1.10^-7^). The low genetic control of the index V shows that in addition to the fact that the interannual density variability is controlled by environment [@becker1995; @huang2007; @Nicault2010; @zaehle2014], its amplitude is also controlled by environment. One hypothesis that can explain the low heritability of the V index is the young age of our trees. Indeed, the study of @Gaspar2008 showed an increase in the heritability of the components of density with age. As a result, we can hope for an increase in the heritability of the index V, which represents the amplitude of the interannual variation in wood density.

Our study can allows identify trees with low variation from pith-to-bark but includes limitations for identifying tree that may have low interannual variation in wood density as part in tree genetic selection. Future studies should focus on the resilience and variability associated with one-time events such as short-term water stress. In addition, the trees used for this study are relatively young, we can be interested in older trees.
